---
title: "Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(RColorBrewer)
library(paletteer)
library(janitor)
library(here)
library(ggmap)
```

```{r}
animal_bites <- readr::read_csv("data/Animal_Bites.csv")%>%clean_names()
```
```{r}
animal_bites
```
#Cleaning up the Data
```{r}
animal_bites <- animal_bites%>%
  naniar::replace_with_na(replace=list(gender_id_desc="UNKNOWN", results_id_desc="UNKNOWN", disposition_id_desc="UNKNOWN", vaccination_date="<NA>", head_sent_date="<NA>", release_date="<NA>"))
animal_bites
```

```{r}
animal_bites%>%
  naniar::miss_var_summary()
```
Most of the results from the rabies test are missing as well as when the sample was sent in to the lab. 

```{r}
animal_bites <- animal_bites%>%
  separate(bite_date, into=c("bite_year", "bite_month", "bite_day"), sep = "-")
animal_bites
```

#Questions we wanted to ask
What are the results of the rabies test? 
```{r}
animal_bites%>%
  count(results_id_desc)
```
```{r}
animal_bites%>%
   filter(results_id_desc!="NA")%>%
  ggplot(aes(results_id_desc, fill=results_id_desc)) + geom_bar() + labs(title="Rabies Test Results", x="Results", y="Number of Reports") + theme_classic()
```
```{r}
animal_bites%>%
  ggplot(aes(results_id_desc, fill=results_id_desc)) + geom_bar() + labs(title="Rabies Test Results (with NA)", x="Results", y="Number of Reports") + theme_classic()
```

What animal is most likely to bite? 

```{r}
animal_bites%>%
  count(species_id_desc)%>%
  arrange(desc(n))
```

```{r}
animal_bites%>%
  select(species_id_desc)%>%
  ggplot(aes(species_id_desc, fill=species_id_desc)) + geom_bar() + labs(title="Bite Reports by Animal Species", x="Species", y="Number of Reports" )
```

What animal has the most positive tests for rabies?
```{r}
animal_bites%>%
  select(species_id_desc, results_id_desc)%>%
  filter(results_id_desc=="POSITIVE")%>%
  count(species_id_desc)
```
```{r}
animal_bites%>%
  select(species_id_desc, results_id_desc)%>%
  filter(results_id_desc=="POSITIVE")%>%
  ggplot(aes(species_id_desc, fill=species_id_desc)) + geom_bar() + labs(title="Positive Cases by Species", x="Species", y="Count") + theme_classic()
```


What breed of dog is most likely to bite?
```{r}
animal_bites%>%
  count(breed)%>%
  arrange(desc(n))
```
```{r}
animal_bites%>%
  ggplot(aes(breed)) + geom_bar() 
```

Where was data collected from? 

```{r}
animal_bites%>%
  count(victim_zip)%>%
  arrange(desc(n))
```
```{r}

```

```{r}
lat <- c(40.381834, 33.583623)
long <- c(-86.770639, -86.770639)
bbox <- make_bbox(long, lat, f=0.05)
```
```{r}
#map1 <- get_map(bbox, maptype = "terrain", source = "stamen")
#ggmap(map1)
```


When was data collected?
```{r}
animal_bites%>%
  count(bite_year)%>%
  arrange(bite_year)
```
```{r}
animal_bites$bite_year <- as.numeric(animal_bites$bite_year)
```

```{r}
animal_bites%>%
  filter(bite_year!="5013")%>%
  filter(bite_year!="2201")%>%
  filter(bite_year!="2101")%>%
  filter(bite_year!="1952")%>%
  ggplot(aes(bite_year, fill=bite_month)) + geom_bar() 
```

Vaccination rates? 
```{r}
animal_bites%>%
  count(vaccination_yrs)
```
```{r}
animal_bites%>%
  filter(vaccination_yrs=="11")
```
```{r}
animal_bites%>%
  filter(results_id_desc=="POSITIVE")
```


Where was the place on the body where most people got bit? 


Associations with positive rabies results. 

#Lessons
PLEASE if you ever go into research and imputing data, be accurate when imputing your data. 
Also try to record your data.
