---
title: "Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(RColorBrewer)
library(paletteer)
library(janitor)
library(here)
```

```{r}
animal_bites <- readr::read_csv("Health_AnimalBites.csv")%>%clean_names()
```
```{r}
animal_bites
```
#Cleaning up the Data
```{r}
animal_bites <- animal_bites%>%
  naniar::replace_with_na(replace=list(gender_id_desc="UNKNOWN", results_id_desc="UNKNOWN", disposition_id_desc="UNKNOWN", vaccination_date="<NA>", head_sent_date="<NA>", release_date="<NA>"))
animal_bites
```

```{r}
animal_bites%>%
  naniar::miss_var_summary()
```
Most of the results from the rabies test are missing as well as when the sample was sent in to the lab. 

```{r}
animal_bites <- animal_bites%>%
  separate(bite_date, into=c("year", "month", "day"), sep = "-")
animal_bites
```

#Questions we wanted to ask
What are the results of the rabies test? 
```{r}
animal_bites%>%
  count(results_id_desc)
```
What animal is most likely to bite? 

```{r}
animal_bites%>%
  count(species_id_desc)%>%
  arrange(desc(n))
```


What animal has the most positive tests for rabies?


What breed of dog is most likely to bite?
```{r}
animal_bites%>%
  count(breed_id_desc)%>%
  arrange(desc(n))
```

Where was data collected from? 


When was data collected?


Vaccination rates/dates? 


Where was the place on the body where most people got bit? 


Associations with positive rabies results. 

