---
title: "Project"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(RColorBrewer)
library(paletteer)
library(janitor)
library(here)
library(ggmap)
```

```{r}
animal_bites <- readr::read_csv("data/Animal_Bites.csv")%>%clean_names()
```
```{r}
animal_bites
```
#Cleaning up the Data
```{r}
animal_bites <- animal_bites%>%
  naniar::replace_with_na(replace=list(gender_id_desc="UNKNOWN", results_id_desc="UNKNOWN", disposition_id_desc="UNKNOWN", vaccination_date="<NA>", head_sent_date="<NA>", release_date="<NA>"))
animal_bites
```

```{r}
animal_bites%>%
  naniar::miss_var_summary()
```
Most of the results from the rabies test are missing as well as when the sample was sent in to the lab. 

```{r}
animal_bites <- animal_bites%>%
  separate(bite_date, into=c("bite_year", "bite_month", "bite_day"), sep = "-")
animal_bites
```

#Questions we wanted to ask
What are the results of the rabies test? 
```{r}
animal_bites%>%
  count(results_id_desc)
```
```{r}
animal_bites%>%
   filter(results_id_desc!="NA")%>%
  ggplot(aes(results_id_desc, fill=results_id_desc)) + geom_bar() + labs(title="Rabies Test Results", x="Results", y="Number of Reports") + theme_classic()
```
```{r}
animal_bites%>%
  ggplot(aes(results_id_desc, fill=results_id_desc)) + geom_bar() + labs(title="Rabies Test Results (with NA)", x="Results", y="Number of Reports") + theme_classic()
```

What animal has the most reported bites? 

```{r}
animal_bites%>%
  count(species_id_desc)%>%
  arrange(desc(n))
```

```{r}
animal_bites%>%
  select(species_id_desc)%>%
  ggplot(aes(species_id_desc, fill=species_id_desc)) + geom_bar() + labs(title="Bite Reports by Animal Species", x="Species", y="Number of Reports" )
```

What animal has the most positive tests for rabies?
```{r}
animal_bites%>%
  select(species_id_desc, results_id_desc)%>%
  filter(results_id_desc=="POSITIVE")%>%
  count(species_id_desc)
```
```{r}
animal_bites%>%
  select(species_id_desc, results_id_desc)%>%
  filter(results_id_desc=="POSITIVE")%>%
  ggplot(aes(species_id_desc, fill=species_id_desc)) + geom_bar() + labs(title="Positive Cases by Species", x="Species", y="Count") + theme_classic()
```


What breed of dog has the most reported bites?
```{r}
animal_bites%>%
  filter(species_id_desc=="DOG")
```

```{r}
top_breed_id <- animal_bites%>%
  filter(species_id_desc=="DOG")%>%
  count(breed_id_desc)%>%
  arrange(desc(n))%>%
  top_n(11)%>%
  filter(breed_id_desc!="NA")
top_breed_id
```

```{r}
top_breed_id%>%
  ggplot(aes(x=breed_id_desc, y=n, fill=breed_id_desc)) + geom_col() +labs(title="Bites by Dog Breed ID", x="Breed ID", y="Number of Bites") + theme_classic() + theme(axis.text.x = element_text(angle = 30, hjust = 1)) 
```
```{r}
top_breed <- animal_bites%>%
  filter(species_id_desc=="DOG")%>%
  count(breed)%>%
  arrange(desc(n))%>%
  top_n(11)%>%
  filter(breed!="NA")
top_breed
```
```{r}
top_breed%>%
  ggplot(aes(x=breed, y=n, fill=breed)) + geom_col() +labs(title="Bites by Dog Breed", x="Breed", y="Number of Bites") + theme_classic() + theme(axis.text.x = element_text(angle = 30, hjust = 1)) 
```

Where was data collected from? 

```{r}
animal_bites%>%
  count(victim_zip)%>%
  arrange(desc(n))%>%
  top_n(10
        )
```

```{r}
zipcodes <- readr::read_csv("data/zipcodes  - Sheet1.csv")%>%
  clean_names()
```

```{r}
zipcodes%>%
  summary()
```

```{r}
lat <- c(38.08, 38.26)
long <- c(-85.86, -85.45)
bbox <- make_bbox(long, lat, f=0.05)
```
```{r}
map1 <- get_map(bbox, maptype = "terrain", source = "stamen")
ggmap(map1)
```
```{r}
ggmap(map1) + geom_point(data=zipcodes, aes(long, lat), color="blue", size=3) + labs(title="Location of Bites Reported", x="Longitude", y="Latitude")
```

When was data collected?
```{r}
animal_bites%>%
  count(bite_year)%>%
  arrange(bite_year)
```
```{r}
animal_bites$bite_year <- as.factor(animal_bites$bite_year)
```

```{r}
animal_bites%>%
  filter(bite_year!="5013")%>%
  filter(bite_year!="2201")%>%
  filter(bite_year!="2101")%>%
  filter(bite_year!="1952")%>%
  filter(bite_year!="2029")%>%
  ggplot(aes(bite_year, fill=bite_month)) + geom_bar() + labs(title="Dates of Data Collection", x= "Bite Year", y="Number of Bites")+ theme_classic() + theme(axis.text.x = element_text(angle=30))
```

Vaccination rates? 
```{r}
animal_bites%>%
  count(vaccination_yrs)
```
```{r}
animal_bites%>%
  filter(vaccination_yrs=="3")
```
```{r}
animal_bites%>%
  filter(results_id_desc=="POSITIVE")
```

```{r}
animal_bites%>%
  select(species_id_desc, vaccination_yrs, results_id_desc)%>%
  filter(species_id_desc=="DOG" | species_id_desc=="CAT"| species_id_desc=="FERRET"|species_id_desc=="HORSE")%>%
  filter(results_id_desc=="POSITIVE" | results_id_desc=="NEGATIVE")
```


#Take Away
PLEASE if you ever go into research and imputing data, be accurate when imputing your data. 
Also try to record your data and not leave things blank.
Also please get your pets vaccinated. 

#Thank you so much! 

